Enhancement of SDR in Thessaloniki

### 2024-03-02 GHI_enh_03_process.tex
Commit 2024-03-02 12:11

\begin{verbatim}
aa
aday
All_daily_ratio_lim
alpha
ampl
avar
BIO_ELEVA
C1_Clearness_Kt_THRES
C1_GLB_diff_THRES
C2_Clearness_Kt_THRES
C3_cs_ref_ratio
C4_cs_ref_ratio
C4_GLB_diff_THRES
C4_lowcut_ratio
C4_lowcut_sza
Clear_daily_ratio_lim
CLEARdir
Cloud_daily_ratio_lim
cols
common_data_13
common_data_14
common_data_14_2
CS_file_13
CS_file_14
CS_file_14_2
csmodel
Daily_aggregation_N_lim
Daily_confidence_limit
daylist
Days_of_year
I1_longterm
I2_szatrend
I3_trendsconsist
ii
Input_data_ID
Kurudz_SC
MIN_ELEVA
MIN_N
Monthly_aggegation_N_lim
Monthly_confidence_limit
my.cols
my.cols.gr
pyear
R_COMPILE_PKGS
RANDOM_SEED
raw_input_data
running_mean_window_days
running_mean_window_years
SEAS_MIN_N
SelEnhanc
SZA_aggregation_N_lim
SZA_BIN
SZA_confidence_limit
variables_fl
yearstodo
ylim
ST_daily
ST_E_daily
ST_E_daily_seas
ST_E_monthly
ST_E_monthly_seas
ST_E_sza
ST_E_sza_monthly
ST_E_yearly
ST_extreme_daily
ST_extreme_monthly
ST_extreme_SZA
ST_extreme_SZA_monthly
ST_extreme_yearly
ST_G0
ST_G1
ST_monthly
ST_sza
ST_sza_monthly
ST_total
ST_yearly
\end{verbatim}

@@

\begin{verbatim}
2024-03-01 17:32:55.6 athan@tyler GHI_enh_03_process.R 2.076944 mins
\end{verbatim}

>>>>

\begin{verbatim}
aa
aday
All_daily_ratio_lim
alpha
ampl
avar
BIO_ELEVA
C1_Clearness_Kt_THRES
C1_GLB_diff_THRES
C2_Clearness_Kt_THRES
C3_cs_ref_ratio
C4_cs_ref_ratio
C4_GLB_diff_THRES
C4_lowcut_ratio
C4_lowcut_sza
Clear_daily_ratio_lim
CLEARdir
Cloud_daily_ratio_lim
cols
common_data_13
common_data_14
common_data_14_2
CS_file_13
CS_file_14
CS_file_14_2
csmodel
Daily_aggregation_N_lim
Daily_confidence_limit
daylist
Days_of_year
Energy_Div
I1_longterm
I2_szatrend
I3_trendsconsist
ii
Input_data_ID
Kurudz_SC
MIN_ELEVA
MIN_N
Monthly_aggegation_N_lim
Monthly_confidence_limit
my.cols
my.cols.gr
pyear
R_COMPILE_PKGS
RANDOM_SEED
raw_input_data
running_mean_window_days
running_mean_window_years
SEAS_MIN_N
SelEnhanc
SZA_aggregation_N_lim
SZA_BIN
SZA_confidence_limit
variables_fl
yearstodo
ylim
ST_daily
ST_E_daily
ST_E_daily_seas
ST_E_monthly
ST_E_monthly_seas
ST_E_sza
ST_E_sza_monthly
ST_E_yearly
ST_extreme_daily
ST_extreme_monthly
ST_extreme_SZA
ST_extreme_SZA_monthly
ST_extreme_yearly
ST_G0
ST_G1
ST_monthly
ST_sza
ST_sza_monthly
ST_total
ST_yearly
\end{verbatim}

@@

\begin{verbatim}
2024-03-02 09:45:10.6 athan@tyler GHI_enh_03_process.R 2.001386 mins
\end{verbatim}

### 2024-03-02 GHI_enh_04_investigate.tex
Commit 2024-03-02 12:11

Units for GLB\_diff.sum : J/m\^{}2lmD: 33660.74 +/- 5692.733

lmY: 33661.3 +/- 5692.832

Arima: 33699.7541 8650.717 3.8956 1e-04

@@

Units for GLB\_diff.sum : J/m\^{}2lmD: 1467.856 +/- 152.6556

@@

Units for GLB\_diff.sum : J/m\^{}2lmD: 368.3616 +/- 253.4977

lmY: 368.3881 +/- 253.5018

Arima: 368.4448 258.2729 1.4266 0.1537

@@

\begin{verbatim}
2024-03-02 09:11:28.2 athan@tyler GHI_enh_04_investigate.R 1.451215 mins
\end{verbatim}

>>>>

Units for GLB\_diff.sum : kJ/m\^{}2lmD: 33.66074 +/- 5.692733

lmY: 33.6613 +/- 5.692832

Arima: 33.7219 8.8826 3.7964 1e-04

@@

Units for GLB\_diff.sum : kJ/m\^{}2lmD: 1467.856 +/- 152.6556

@@

Units for GLB\_diff.sum : kJ/m\^{}2lmD: 0.3683616 +/- 0.2534977

lmY: 0.3683881 +/- 0.2535018

Arima: 0.3684 0.2583 1.4266 0.1537

@@

\begin{verbatim}
2024-03-02 09:46:24.0 athan@tyler GHI_enh_04_investigate.R 0.976988 mins
\end{verbatim}
